### 2017-12-11 submission/supplemental.Rmd
fix titles table s5 and s6
add table s7 and s8

**Table S5: Kruskal-Wallis Results of Number of OTUs Differences between HiFi Taq in Mock Samples**

@@

**Table S6: **

@@

**Table S7: **

@@

@@

>>>>

**Table S5: Kruskal-Wallis Results of Per Base Error Rate Differences between HiFi Taq in Mock Samples**

@@

**Table S6: Dunn's Post-Hoc Results of Per Base Error Rate between HiFi Taq in Mock Samples**

@@

**Table S7: Kruskal-Wallis Results of Sequences with Error Differences between HiFi Taq in Mock Samples**

@@

mock_error_count_kruskal <- as.data.frame(
  read_csv("../data/process/tables/mock_error_count_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  filter(sub_sample_level > 500)

colnames(mock_error_count_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle", "Sub-Sample Depth")

kable(mock_error_count_kruskal, format = "markdown", align = 'c', padding = 2)

@@

**Table S8: Dunn's Post-Hoc Results of Sequences with Error Differences between HiFi Taq in Mock Samples**

```{r supplemental_table8, echo=FALSE, message=FALSE, warning=FALSE}

mock_error_count_dunn <- as.data.frame(read_csv("../data/process/tables/mock_error_count_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(sub_sample_level > 500, pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh)

colnames(mock_error_count_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle", "Sub-Sample Depth")

kable(mock_error_count_dunn, format = "markdown", align = 'c', padding = 2)
